\boldmath Heavy resonances at energy-frontier hadron colliders

### 2019-02-22 paper_epjc.tex
Updates from Overleaf

\documentclass[pdftex,twocolumn,epjc3]{svjour3}          % twocolumn

\RequirePackage[T1]{fontenc}

@@

\title{Insert your title here\thanksref{t1}}

\subtitle{Do you have a subtitle?\\ If so, write it here}

\author{First Author\thanksref{e1,addr1}
        \and
        Second Author\thanksref{e2,addr2,addr3} %etc.
}

\thankstext[$\star$]{t1}{Thanks to the title}
\thankstext{e1}{e-mail: magic1@xxx.xx}
\thankstext{e2}{e-mail: magic2@xxx.xx}

\institute{First Address, Street, City, Country\label{addr1}
          \and
          Second Address, Street, City, Country\label{addr2}
          \and
          \emph{Present Address:} Street, City, Country\label{addr3}
}

@@

\begin{abstract}
Insert your abstract here. Insert your abstract here. Insert your abstract here.
Insert your abstract here. Insert your abstract here. Insert your abstract here.
Insert your abstract here. Insert your abstract here. Insert your abstract here.
\end{abstract}

>>>>

\documentclass[pdftex,twocolumn,epjc3]{svjour3}          % twocolumn
\usepackage{commands}
\RequirePackage[T1]{fontenc}

@@

\title{\boldmath Heavy resonances at energy-frontier hadron colliders}

%\subtitle{Do you have a subtitle?\\ If so, write it here}

\author{David~Jamin\thanksref{e1,addr1,addr3}
        \and
        Clement~Helsens\thanksref{e2,addr1}
        \and
        Michelangelo~L.~Mangano\thanksref{e3,addr1}
        \and
        Thomas~G.~Rizzo\thanksref{e4,addr2}
        \and
        Michele~Selvaggi\thanksref{e5,addr1}
}

%\thankstext[$\star$]{t1}{Thanks to the title}
\thankstext{e1}{e-mail: david.jamin@cern.ch}
\thankstext{e2}{e-mail: clement.helsens@cern.ch}
\thankstext{e3}{e-mail: michelangelo.mangano@cern.ch}
\thankstext{e4}{e-mail: rizzo@slac.stanford.edu}
\thankstext{e5}{e-mail: michele.selvaggi@cern.ch}

\institute{CERN, CH-1211 Geneva 23, Switzerland\label{addr1}
          \and
          SLAC National Accelerator Laboratory 2575 Sand Hill Rd., Menlo Park, CA, 94025 USA\label{addr2}
          \and
          Academia Sinica, Institute of  Physics, Taipei, Taiwan\label{addr3}
}

@@

\begin{abstract}
This paper explores the physics reach of the proton-proton Future Circular Collider (FCC-hh) and of the High-Energy LHC (HE-LHC) for searches of new particles produced in the $s$ channel and decaying to two high-energy leptons, jets (non-tops), tops or W/Z bosons. We discuss the expected discovery potential and exclusion limits for benchmark models predicting new massive particles that result in resonant structures in the invariant mass spectrum. We also present a detailed study of the HE-LHC potential to discriminate among different models, for a $\Zp$ that could be discovered by the end of High-Luminosity LHC (HL-LHC).
\end{abstract}

\input{paper_text}
